EuPPollNet: A European database of plant-pollinator networks

### 2024-05-25 Manuscript/EuPPollNet_Ms.qmd
edits

Despite this database covering a wide range of habitats across `r country_number` European countries, some areas such as Eastern Europe and the Mediterranean region are evidently under-represented. This reflects the lack of plant-pollinator community data in highly relevant regions of pollinator diversity [REFs] and could help explain the limited taxonomic coverage found of plant and pollinator species at the European level. This is especially relevant as Eastern Europe is expected to continue developing and use their vast natural resources [@bennett2018] and the Mediterranean region is likely to be severely impacted by climate change [@jaworski2022; @duchenne2020; @pareja2023]. Although some of the most well studied countries in Europe (e.g., Belgium or The Netherlands) seem to have suffered most of the plant and pollinator biodiversity loss at the end of the 20th century [@carvalheiro2013], plant-polllinator communities in Europe and across the globe still suffer from major threads such as climate change [REFs], land use change [REFs], or the introduction of alien species [@vila2009; @vanbergen2018].

@@

Link with interactions -->

More species less connectance, which increases the number of missing links.

networks condense information but this workflow allo possibility to explore species phenology... and more

Interactions:
Sampling area, spp accumulation vs interactions:
https://doi.org/10.1890/12-0367.1
Sampling completeness 
 [e.g., @chacoff2012]

@@

@@

foundation for future work

Geographic and taxonomic biases!
Supporting reference:
https://doi.org/10.1111/ecog.05926

>>>>

Despite this database covering a wide range of habitats across `r country_number` countries, it contains geographical biases that can impact our understanding of plant-pollinator communities [@hughes2021]. For instance, most plant-pollinator networks belongs to central Europe, while Eastern Europe and the Mediterranean region are under-represented. This is consistent with previous studies which also report lack of plant-pollinator data for those regions [REFs], highlighting that this database reflects existing patterns in data availability despite the absence of a systematic search for studies. This is especially relevant as Eastern Europe is expected to continue developing and use their vast natural resources [@bennett2018], and the Mediterranean region is likely to be severely impacted by climate change [@jaworski2022; @duchenne2020; @pareja2023]. These areas are well known for their rich pollinator diversity, and their under-representation is likely contributing to the low taxonomic coverage of this database.

@@

@@

**Maybe for the concluding paragraph**:

Although some of the most well studied countries in Europe (e.g., Belgium or The Netherlands) seem to have suffered most of the plant and pollinator biodiversity loss at the end of the 20th century [@carvalheiro2013], plant-polllinator communities in Europe and across the globe still suffer from major threads such as climate change [REFs], land use change [REFs], or the introduction of alien species [@vila2009; @vanbergen2018].

@@
